\chapter{Research Design}
\label{chapter:Research Design} 

This chapter elaborates the used research and analysis methods, presents interview themes and structures, and evaluates the research. 

\subsection{Initial Research}
This research aims to understand the requirements from multiple companies towards common data standards. The research began with reviewing relevant literature on data governance, sharing inter-enterprise data, knowledge sharing and institutional theory. The literature review was conducted by keywoard search in scientific databases, and citations backwards and forwards were used within relevant literature. In all disciplines the scope was kept on general level. This initial literature review formed the basis for the interview themes.

\subsection{Interview Themes}
The interview is a semi-structured thematic interview \cite{hirsjarvi2000tutkimushaastattelu} with a standardized set of open-ended questions, which allows deep exploration of studied objects \cite{patton2002qualitative}. The interviews are performed once per interviewee, with one to two interviewees per participating company. The interview themes are presented in the appendices.

The interview themes were formulated by the researcher based on findings of the initial literature research. The interviews aimed to understand the requirements and capabilities of the organizations in multiple different areas. The interview themes included the following themes for following reasons:

\begin{itemize}  
\item \textit{Background information} of the interviewee and the organization to position the answers and analysis.
\item \textit{Institutional barriers}: to understand the regulative, normative and cognitive barriers that prevent an organization from sharing data in the study setting.
\item \textit{Business goals}: to understand the motivation of participating companies to take part in the collaboration. 
\item \textit{Data quality}: to understand the state of the companys data and their perception on the importance, possibilities and risks of its quality. 
\item \textit{Data lifecycle management}: to determine how companies understand the process of data flows.
\item \textit{Data security and access management}: to determine the importance, requirements and current state of the topic. 
\item \textit{Data ownership and governance}: to understand what concerns and constraints the companies have towards ownership of the data.
\item \textit{Business models}: to understand when companies would consider applying shared data models.
\end{itemize}

All of the interview themes were not discussed in detail with each interviewee, depending on their role in the organization. The interviews were done in Finnish, since that is the mother language of all interviewees. 

\subsection{Conducting Interviews}
Interviewees were sampled with convenience sampling based on their role in their organization, participation in the research setting and proximity to the researcher. The interviewees were contacted individually by e-mail, where the purpose and topics of the interview were given and a suitable time was agreed. Before each interview, the researcher introduced himself and the fields of study of the research, and informed the interviewee of ethical manners and consent. The consent form stated that all of the information will be handed with confidence and anonymity, so that a particular interviewee or organization cannot be identified. In addition, only the researcher has access to the data. The interviews were also audio recorded for further analysis, and the interviewees informed of the matter.

During the interview, the researcher took handwritten notes to support analysis, and interpreted insights immediately after the interview. After the interview, voice records were later transcribed for data analysis. A total of 7 interviews were conducted within 5 different companies participating in the research setting. Interviewees included directors of different business functions related to IoT, digital strategy, quality management and development management.

TODO: tässä voisi kuvata taulukossa haastattelujoukon

\subsection{Case Study}
Case study is a way to collect data through observation and to test theories in an unmodified setting. The linkage with empirical evidence makes case study research likely to have strengths such as novelty, testability and empirical validity \cite{eisenhardt1989building}. Case studies can be divided into four different purposes: Exploratory, Descriptive, Explanatory and Improving \cite{robson2016real}. An exploratory case study seeks new insights, finds out what is happening, and generates ideas and hypotheses for new research. Descriptive case study attempts to portray a situation or a phenomenom. An explanatory case study attempts to seek an explanation to a problem or a situation, mostly in a causal relationship. Finally, an improving case study tries to improve an aspect of the studied phenomenom.

Different approaches to the order of data collection, analysis and generalization can be categorized into inductive, deductive and abductive approaches \cite{dubois2002systematic}. An inductive approach moves from data to theory, and begins by first collecting the data, and then looking for patterns and forming theories that explain those patterns. A deductive approach is in reverse order. An abductive approach starts with the consideration of facts or particular observations, which are then used to form hypotheses that relate them to a fact or a rule that accounts for them. The facts are therefore correlated into a more general description, that relates them to a wider context.

Sampling

Structure \cite{eisenhardt1989building}

Triangulation

This study is an exploratory inductive study, 

\subsection{Qualitative research}


\subsection{Data analysis}

Data analysis was done based on template analysis, which is a way to thematically organize and analyze qualitative data \cite{king1998template}. The research data consisted of transcribed voice records of 7 interviews and personal notes. Additional material was also provided by the organizations on demand, and was helpful for understanding and validating concepts during the analysis. The data was iteratively categorized through coding into families based on the interview themes and research questions, such as barriers, data quality, business models, data lifecycle management and data governance. 

\subsection{Limitations of the Research}




%Metodit
%	- Kvalitatiivinen case-tutkimus tuettuna kvantitatiivisella kyselyllä
%	- Kuinka kerätään dataa, kuinka analysoidaan dataa

