\chapter{Findings and Analysis}

This chapter presents and analyses the findings of the research. The findings are organized as follows: first, the barriers to sharing data from all participanting organizations are presented. Then, 


\label{chapter:results}

%You have now explained how you are going to tackle your problem. 
%Go do that now! Come back when the problem is solved!

%Now, how did you solve the problem? 
%Explain how you implemented your solution, be it a software component, a
%custom-made FPGA, a fried jelly bean, or whatever.
%Describe the problems you encountered with your implementation work.


\subsection{Barriers}
1. Not sure which parties to include
2. Afraid of losing competitive advantage:
	-Does coopetition beat competition?
	-How to balance own advantage?
3. Understanding. What data, to whom, why, how?
4. Historical and cultural barriers
5. Lacking practices and contract models

\subsubsection{Barrier 1: Data close to core IPR}

"Some data can be sensitive, such as planning information, and it goes close to the vendors core IPR. If a country with lower cost of labour gets access to this information, nothing prevents distortion of competition."
-Supplier 1


"Supplier 1 and 2 operate with our competitors in other countries. Can our competitors learn from the data we share to our suppliers?"
-Manufacturer


\subsubsection{Barrier 2: Culture of coopetition}


\subsubsection{Barrier 3: New business model}

"It is a large cultural shift, and the ship turns slowly. If we could see the benefits (in sharing data) it would help, but today they're still vague."
-Supplier 2

\subsubsection{Barrier 4: Unclear setup of the value chain}
As response to What factors in your organization prevent sharing data and why?: "Understanding of where data is shared, why it is shared, and how we profit from sharing.".
-Supplier 4

\subsubsection{Barrier 5: Data security}




\begin{center}
    \begin{tabular}{ | l | l | l | p{5cm} |}
    \hline
    Barrier & Suppliers & Manufacturer
    Monday & 11C & 22C & A clear day with lots of sunshine.  
    Supplier 1: Valmet & Supplier 2: ABB & Supplier 3: Efora & Supplier 4: Metso & Manufacturer: Stora Enso\\ \hline
    yes & yes & yes & no & no\\ \hline
    \hline
    \end{tabular}
\end{center}


\subsection{Support}

1. Business opportunities:
which, what, how?


2. Technological advancements has made sharing data possible
3. Whole society moving to this direction
4. More business opportunities

%TODO: tuo PLATFORM-kulmaa
%OPERATIONS-näkökulma mukaan





TODO: tuo google drivesta löydökset